Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
edit map

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
library(magick)
```

@@

## Google Trends Map

```{r, echo=FALSE, message=FALSE}
image_read("https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Paper/gtrends_map.png")
```
